\chapter{Sample Consent Forms}

\section{Sample Informed Consent Template for Participants with Mild Cognitive Impairment}

\subsection{Study Title}
Clinical Trial of [Application Name]: A Digital Memory Support Tool for People with Mild Cognitive Impairment or Early-Stage Alzheimer's Disease

\subsection{Introduction}
You are being invited to take part in a research study to test a digital application designed to help people with memory difficulties. This document provides important information about the study. A member of the research team will discuss this information with you and answer any questions you may have.

\subsection{Purpose of the Study}
We are testing a digital application (computer/tablet program) that is designed to help people remember important information and past memories. We want to find out if using this application improves quality of life and helps with memory problems.

\subsection{What Will Happen in This Study}
If you agree to participate:
\begin{enumerate}
    \item You will be randomly assigned (like flipping a coin) to either use the digital memory application or continue with your usual activities without the application for [duration] weeks.
    
    \item If you are assigned to use the application:
    \begin{itemize}
        \item We will provide you with [device description] to use during the study
        \item We will show you how to use the application
        \item We will ask you to use the application for at least [frequency] times per week
        \item We or your caregiver will help add personal photos and information to the application
    \end{itemize}
    
    \item Everyone in the study will:
    \begin{itemize}
        \item Complete tests of memory and thinking at the beginning, middle, and end of the study (each testing session takes about 1 hour)
        \item Answer questions about your mood, daily activities, and quality of life
        \item Have a caregiver complete questionnaires about your everyday functioning
    \end{itemize}
    
    \item After the study ends, if you were in the group that did not receive the application, you will have the opportunity to use it if you wish.
\end{enumerate}

\subsection{Possible Benefits}
You may experience improvements in your memory, mood, or quality of life from using the application. However, we cannot guarantee that you will benefit from participating in this research. The information we learn may help develop better tools for people with memory problems in the future.

\subsection{Possible Risks and Discomforts}
The risks of participating in this study are minimal. Potential discomforts include:
\begin{itemize}
    \item You may feel tired or frustrated during memory testing or while learning to use the application
    \item You may feel sad or upset when viewing certain personal memories
    \item There is a small risk that confidential information could be accidentally disclosed, though we have strong protections in place
\end{itemize}

\subsection{Privacy and Confidentiality}
We will protect your personal information by:
\begin{itemize}
    \item Using secure, encrypted storage for all data
    \item Giving you a unique code number and removing your name from most study records
    \item Restricting access to identifiable information to authorized study staff
    \item Following all applicable privacy laws
\end{itemize}

\subsection{Your Rights}
Participation in this study is completely voluntary. You can:
\begin{itemize}
    \item Decide not to participate
    \item Leave the study at any time
    \item Skip any questions you don't want to answer
    \item Refuse any tests you don't want to complete
\end{itemize}
Your decision will not affect your medical care or any services you receive.

\subsection{Contact Information}
If you have questions or concerns, please contact:
\begin{itemize}
    \item Study Principal Investigator: [Name, Phone, Email]
    \item Research Coordinator: [Name, Phone, Email]
    \item For questions about your rights as a research participant: [IRB Contact Information]
\end{itemize}

\subsection{Consent Statement}
By signing below, I confirm that:
\begin{itemize}
    \item I have read (or had read to me) this consent form
    \item The study has been explained to me
    \item My questions have been answered
    \item I voluntarily agree to participate
\end{itemize}

\vspace{1cm}
\begin{tabular}{p{7cm}p{7cm}}
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\
Participant's Signature & Date \\[1.5cm]
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\
Printed Name of Participant & \\[1.5cm]
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\
Signature of Person Obtaining Consent & Date \\[1.5cm]
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ & \\
Printed Name of Person Obtaining Consent & \\
\end{tabular}

\section{Sample Surrogate Informed Consent Template}

\subsection{Study Title}
Clinical Trial of [Application Name]: A Digital Memory Support Tool for People with Alzheimer's Disease

\subsection{Introduction}
Your family member is being invited to participate in a research study testing a digital application designed to help people with memory difficulties. As their legally authorized representative, you are being asked to consider whether they should take part. This document provides important information about the study. A member of the research team will discuss this information with you and answer any questions.

\subsection{Purpose of the Study}
We are testing a digital application that is designed to help people with Alzheimer's disease connect with their personal memories and important information. We want to determine if using this application improves quality of life, mood, and behavior.

\subsection{Assessment of Participant Capacity}
We have determined that your family member is unable to provide fully informed consent for this research due to their cognitive impairment. However, we will still seek their assent (agreement) to participate and will respect any indication that they do not wish to continue.

\subsection{What Will Happen in This Study}
If you agree to your family member's participation:
\begin{enumerate}
    \item They will be randomly assigned to either use the digital memory application or continue with usual activities for [duration] weeks.
    
    \item If assigned to use the application:
    \begin{itemize}
        \item We will provide the necessary equipment
        \item We will train you and your family member on using the application
        \item We will ask that the application be used at least [frequency] times per week
        \item You will help add personal photos and information to the application
    \end{itemize}
    
    \item Throughout the study:
    \begin{itemize}
        \item Your family member will complete assessments of memory, thinking, mood, and quality of life
        \item You will complete questionnaires about their behavior and functioning
        \item We will collect information about how the application is used
    \end{itemize}
\end{enumerate}

\subsection{Possible Benefits and Risks}
Possible benefits include improved mood, reduced agitation, or enhanced quality of life for your family member. Risks are minimal but may include frustration with technology, emotional responses to memories, or privacy concerns, which we have measures to address.

\subsection{Your Responsibilities as a Surrogate Decision Maker}
As the legally authorized representative, you should:
\begin{itemize}
    \item Make decisions based on what you believe your family member would want
    \item Consider their previously expressed wishes about research participation
    \item Continue to involve them in decisions to the extent possible
    \item Notify researchers if you observe any signs of distress or unwillingness to participate
\end{itemize}

\subsection{Contact Information and Signatures}
[Similar to participant consent form]

\section{Sample Assent Form for Participants with Cognitive Impairment}

\subsection{Simple Explanation of the Study}
We are testing a computer program that might help people remember things better. We want to know if you would like to try using it.

\subsection{What You Would Do}
\begin{itemize}
    \item Try using a special program on a tablet computer
    \item Look at pictures and stories about your life
    \item Answer some questions about how you feel
    \item Spend about 20 minutes using the program a few times each week
\end{itemize}

\subsection{It's Your Choice}
\begin{itemize}
    \item You can say yes or no
    \item You can stop at any time
    \item No one will be upset if you don't want to do it
    \item Your care will not change either way
\end{itemize}

\subsection{Assent Statement}
\begin{itemize}
    \item The study has been explained to me
    \item I understand what I will be asked to do
    \item I agree to participate in this study
\end{itemize}

\vspace{1cm}
[Signature section simplified for participants with cognitive impairment]